---
title: "Statistical Inference Course Project Part2"
author: "Atsuko Yamamoto"
date: "January 24, 2015"
output: pdf_document
---
# Part2 Basic inferential data analysis.
## 1. Load the ToothGrowth data and perform some basic exploratory data analyses
```{r}
setwd("~/Rdata/Inference")
library(datasets)
data(ToothGrowth)
```
## 2. Provide a basic summary of the data.
```{r}
str( ToothGrowth)
summary(ToothGrowth)
table(ToothGrowth$supp,ToothGrowth$dose)
# barplot
library(ggplot2)
par(mfrow = c(1, 2))
boxplot(len ~ dose, data=ToothGrowth,subset = supp == "VC", col = "yellow", main="VC", xlab = "Vitamin C dose mg", ylab = "tooth length", ylim = c(5, 35))
boxplot(len ~ dose, data=ToothGrowth,subset = supp == "OJ", col = "orange", main="OJ", xlab= "Vitamin C dose mg", ylab = "tooth length", ylim = c(5, 35))
```
## 3. Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. (Only use the techniques from class, even if there's other approaches worth considering)

We used t.test in order to perform confidence intervals.
First, comparing whether there is a difference in the growth of the teeth depending on the type of supplement "OJ" or "VC".

```{r}
t.test(len ~ supp, data=ToothGrowth, var.equal=TRUE)
```
The p-value is 0.06. We can not reject the null hypothesis that  Growth of teeth there is a difference depending on the type of supplements.
```{r}
t.test(ToothGrowth$len[ToothGrowth$dose==0.5], ToothGrowth$len[ToothGrowth$dose==1], var.equal=TRUE)
t.test(ToothGrowth$len[ToothGrowth$dose==0.5], ToothGrowth$len[ToothGrowth$dose==2], var.equal=TRUE)
t.test(ToothGrowth$len[ToothGrowth$dose==1], ToothGrowth$len[ToothGrowth$dose==2], var.equal=TRUE)
```
For all three dose level pairs, the p-value is less than 0.05. The mean tooth length increases on raising the dose level. This indicates that we can reject the null hypothesis, and establish that increasing the dose level leads to an increase in tooth length.

## 4. State your conclusions and the assumptions needed for your conclusions.

conclusion

It can not be said that the growth of the tooth is relevant to two types of supplements.
It can be said  a 5% significance level statistically, the intake of vitamin C  is relevant to growth of teeth.

assumption

To prove the assumption that growth of teeth was relevant to the type of supplement, We made a null hypothesis that there is no relevance to growth teeth and the type of supplement  tried to reject .

To prove the assumption that intake of vitamin C  was relevant to growth of teeth, we made a null hypothesis that there is no relevance to the intake  of vitamin C and tooth growth. 
